---
title: "Interactive Map with Leaflet"
author: "Lukhanyiso Bavuma"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(leaflet)
```

## Exploring the World with Leaflet

This interactive map was created on **`r format(Sys.Date(), '%B %d, %Y')`** using R Markdown and the Leaflet package.

### Featured Locations

Below is an interactive map showcasing some of the world's most iconic landmarks. Click on the markers to learn more about each location!

```{r map}
# Create a leaflet map with multiple markers
leaflet() %>%
  addTiles() %>%
  # Eiffel Tower, Paris
  addMarkers(lat = 48.8584, lng = 2.2945,
             popup = "<b>Eiffel Tower</b><br/>Paris, France<br/>Iconic iron lattice tower") %>%
  # Statue of Liberty, New York
  addMarkers(lat = 40.6892, lng = -74.0445,
             popup = "<b>Statue of Liberty</b><br/>New York, USA<br/>Symbol of freedom") %>%
  # Great Wall of China
  addMarkers(lat = 40.4319, lng = 116.5704,
             popup = "<b>Great Wall of China</b><br/>China<br/>Ancient fortification") %>%
  # Sydney Opera House
  addMarkers(lat = -33.8568, lng = 151.2153,
             popup = "<b>Sydney Opera House</b><br/>Sydney, Australia<br/>Performing arts center") %>%
  # Machu Picchu, Peru
  addMarkers(lat = -13.1631, lng = -72.5450,
             popup = "<b>Machu Picchu</b><br/>Peru<br/>Ancient Incan citadel") %>%
  # Table Mountain, South Africa
  addMarkers(lat = -33.9628, lng = 18.4098,
             popup = "<b>Table Mountain</b><br/>Cape Town, South Africa<br/>Flat-topped mountain") %>%
  # Set the view to show all markers
  setView(lng = 0, lat = 20, zoom = 2)
```

### About This Map

This map uses the Leaflet JavaScript library through R to create an interactive visualization. You can:

- **Zoom in/out** using the + and - buttons or your mouse wheel
- **Pan** by clicking and dragging the map
- **Click markers** to see information about each location
- **Switch views** using the layer control

---

*Created with R Markdown and Leaflet for the Developing Data Products course on Coursera.*
```